How to Schedule Periodic Messages in a Network Without Congestion

### 2017-06-02 article/article.tex
noms fig1
petites corrections

This algorithm, contrarily to the previous one, may work well, even when the condition $P \geq 3n\tau$ is not true.
In fact, experimental data in Subsection~\ref{sec:exp_PAZL} suggests that the algorithm finds a solution on average when $P \geq 1.5 n\tau$.
Note that we also experimented with other greedy algorithms which do not use macro-slots, they work even better in practice but their theoretical upper bound is worse.

@@

    \section{Experimental Evaluation}\label{sec:exp_PAZL}

@@

      In this regime, the performances of Shortest-Longest are abysmal since it depends on the difference between the longest and the smallest route
      which is large here. On the other hand, the greedy algorithm has a performance not very different from the case of short routes, which is expected since it does not depends on the size of the route.  \todo{Ajouter la moyenne pour la comparer aux routes courtes}

@@

	\paragraph{Particular cases}

@@

     \subsubsection{A first approach}

@@

     \subsubsection{Sending order}

@@

     For the rest of the section, we look at the different algorithm suggested to improve the second part of the scheduling, after having set the sending order.
      \subsubsection{About the periodicity}
     The previous algorithm is a greedy heuristic, which does not take the period into account. 
     We propose an improved version of the algorithm, still greedy, but which tries to compute some solution that satisfies the period $P$: When we try to schedule some messages $P$ slots after the first message scheduled, the algorithm mind the already scheduled messages, and avoid collisions with them.

@@

     \subsubsection{Near from scheduling problems}

@@

     \subsubsection{Final algorithm}

@@

    \subsubsection{Results}

@@

    \paragraph{Comparer optimal + depart random avec stochastique}

@@

   \begin{itemize}
    \item FPT algorithms for PAZL and PALL 
    \item average latency instead of maximal latency
    \item trees
    \item cycles 
    \item preemption (messages can be cut into pieces)
    \item routes are not given and can be chosen
   \end{itemize}

>>>>

This algorithm, contrarily to the previous one, may work well, even when the condition $P \geq 3n\tau$ is not true.
In fact, experimental data in Subsection~\ref{sec:exp_PAZL} suggests that the algorithm finds a solution on average when $P \geq 2 n\tau$.
Note that we also experimented with other greedy algorithms which do not use macro-slots, they work even better in practice but their theoretical upper bound is worse.

@@

    \subsection{Experimental Evaluation}\label{sec:exp_PAZL}

@@

      In this regime, the performances of Shortest-Longest are abysmal since it depends on the difference between the longest and the smallest route
      which is large here. On the other hand, the greedy algorithm has a performance not so far from the case of short routes, which is expected since it does not directly depend on the size of the route. When repeating the experiments of the previous section on routes of arbitrary length, we find that on average the greedy algorithm finds a solution if $P > 1.89n\tau$.

@@

	\subsection{Particular cases}

@@

     \subsection{A first approach}

@@

     \subsection{Sending order}

@@

     For the rest of the section, we look at the different algorithm suggested to improve the second part of the scheduling, after having set the sending order.
      \subsection{About the periodicity}
     The previous algorithm is a greedy heuristic, which does not take the period into account. 
     We propose an improved version of the algorithm, still greedy, but which tries to compute some solution that satisfies the period $P$: When we try to schedule some messages $P$ slots after the first message scheduled, the algorithm mind the already scheduled messages, and avoid collisions with them.

@@

     \subsection{Using a scheduling algorithm}

@@

     \subsection{Final algorithm}

@@

    \subsection{Results}

@@

    \todo{Comparer optimal + depart random avec stochastique}

@@

   We plan to generalize our study of the PALL problem to more topology,
   such as trees and cycles which are the most common ones in real networks. 
   We would like to design FPT algorithms in the number of routes for PAZL and PALL on the star topology, eventually by relaxing the contraint on the maximal process time into an constraint on the average process time, which seems much more tractable. 
   Moreoever we could allow preemption, that is the messages are allowed to be cut into pieces,
   which could certainly change the complexity of the problem. 
   Finally, the routes may not be fixed but chosen to optimize the latency, which would make the problem even more difficult ( maybe $\Pi_2$-complete instead of $\NP$-complete).
